Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-02-01 docs/ACM/paper.tex
Added references, citations and skeleton to section 3.4

Annotation systems have risen to a place of prominence as a simple and
effective means to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
Tareador~\cite{Ayguade15}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
%\guido{What do you mean by modern accelerators? Not clear.}
Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
to substantial performance gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
%\guido{Suppport what?}
Nevertheless, although convenient, the use of annotations is not straightforward, 
and still lacks supporting tools that help programmers to check if annotations
are correct and/or effective.
%replaced:
%Yet, even if convenient,

@@

@@

>>>>

Annotation systems have risen to a place of prominence as a simple and
effective means to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
Tareador~\cite{Ayguade15}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
%\guido{What do you mean by modern accelerators? Not clear.}
Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
to substantial performance gains~\cite{Sura16Performance, Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
%\guido{Suppport what?}
Nevertheless, although convenient, the use of annotations is not straightforward, 
and still lacks supporting tools that help programmers to check if annotations
are correct and/or effective.
%replaced:
%Yet, even if convenient,

@@

Although the OpenMP runtime guarantees correctness, its scheduling policy
is heavily jeopardized by the excessive queueing up of tasks. Specifically, algorithms
such as \emph{SparseLU} and \emph{FFT} can suffer bloat because of
too many tasks in the Task Graph.  \cite{Kenjiro17}.

\pedro{In the Kenjiro's paper: "This scheduling policy suffers in two situations: 
(1) the parent is a long for loop creating a large number of children, 
all these children cannot start until the parent finishes the task-generating loop (SparseLU); 
(2) binary recursions that, rightly, spawn only the first recursive call as a task (FFT). 
It imposes an upper bound for the ready task queue of a worker; a worker 
is discouraged to create too many tasks ready on the queue"}.

To solve this problem, we conservatively limit the number of tasks
that can be created tied to the same Task Region. We do that by two means:
(1) limiting the creation of recursive tasks by depth; (2) limiting the creation of 
tasks in the whole program.

Consider the FFT example, shown in Figure X.

\pedro{Show FFT example}

\pedro{Explain that the setting is conservative and thus the parameter of control
(max recursion depth and total number of tasks) can be easily switched by the
user, or even completely disabled.}

@@

\pedro{As future work, we plan on performing Autotuning on {\Taskminer} to find good default parameters.
Autotuning works for data-flow applications have been already done in \cite{Trancoso17, Emani15}}.
